Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-09 draft.tex
damnit

Our work here relies on a concrete and convenient model for these enveloping $\EE_n$ algebras by factorization algebras.
In particular, thanks again to \cite{Knudsen}, 
we know that the $\EE_n$ enveloping algebra $\UU_n \fg$ admits a model $\bU_n \fg$ whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^*(V) \otimes \fg)$ to each open set~$V$.
There is another factorization algebra whose underlying assigns $\clies(\Omega^*(V) \otimes \fg)$ to each open~$V$.
Our paper shows that such factorization algebras model other important $\EE_n$ algebras, notably centralizers.

\begin{thm}
\label{thm: centralizer}
Let $\fg$ and $\fh$ be $L_\infty$ algebras over the real or complex numbers, 
and let $f: \fg \rightsquigarrow \fh$ be a homotopy-coherent morphism of $L_\infty$ algebras
(i.e., a map of conilpotent cocommutative coalgebras $f: \cliels(\fg) \to \cliels(\fh)$).
This map determines functorially a map of $\EE_n$ algebras
\[
\UU_n f: \UU_n \fg \to \UU_n \fh
\]
between their enveloping $\EE_n$ algebras.
The centralizer of this map ${\frak Z}_n(\UU_n f)$ is an $\EE_n$ algebra modeled by the factorization algebra 
\[
\clies(\Omega^* \otimes \fg, \cliels(\Omega^*_c \otimes \fh)_f)
\]
equipped with a convolution-type product,
where the subscript $f$ indicates how $\cliels(\Omega^*_c \otimes \fh)$ is a module over $\Omega^* \otimes \fg$.
\end{thm}

@@

\begin{cor}
\label{thm: center}
The center ${\frak Z}_n(\fg)$ of the enveloping $\EE_n$ algebra $\UU_n\fg$ is the $\EE_n$ algebra $\clies(\fg, \UU_n\fg)$. 
When $k$ is $\RR$ or $\CC$, the 
center is modeled by the locally constant factorization algebra that assigns
\[
\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
\]
to each open set $U \subset \RR^n$.
\end{cor}

This result generalizes the fact that $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$, 
since the associative algebra $U\fg$ is modeled by the locally constant one-dimensional factorization algebra that assigns
$\cliels (\fg \otimes \Omega^*_c(U))$ to each open $U \subset \RR$.

@@

\begin{cor}
\label{thm: koszul duality}
The centralizer of the augmentation $\epsilon: \UU_n \fg \to k$ is equivalent to $\clies(\fg)$ viewed as an $\EE_n$ algebra. It is modeled by the locally constant factorization algebra that assigns
\[
\clies(\fg \otimes \Omega^*(V))
\]
to each open set $V \subset \RR^n$.
\end{cor}

@@

Having an explicit presentation for the centralizer of a map of $\EE_n$ algebras leads to a calculation of factorization homology.
The enveloping $\EE_n$ algebra is the homotopy $O(n)$-fixed points, or a $\mathrm{Disk}_n$ algebra in the sense of~\cite{AF},
and hence determines a factorization algebra on any un-oriented $n$-dimensional manifold \cite{Knudsen}.
Therefore, for a closed $n$-dimensional manifold $M$, one has
\[
\int_M {\frak Z}_n(\UU_n \rho) \simeq \clies(\fg \otimes \Omega^*(M), \cliels( \fh \otimes \Omega^*(M))).
\]
Since $\Omega^*(S^n) \simeq \CC[\epsilon_n]$, where $\epsilon_n$ is a formal variable with $|\epsilon_n| = n$ and $\epsilon_n^2 = 0$, we have
\[
\int_{S^n} {\frak Z}_n(\UU_n \rho) \simeq \clies(\fg[\epsilon_n], \cliels( \fh[\epsilon_n]))
\]
For $n=1$, this recovers a theorem of Tamarkin and Tsygan \cite{TT} on the Hochschild cohomology of differential operators on a Lie group $G$;
see Example~\ref{eg: TT}.

@@

\begin{thm}[\cite{LurieHA} Proposition 5.4.5.15]
\label{thm:lurie0} 
There is a fully faithful embedding of $\infty$-categories
\[
{\rm Alg}_{\EE_n} \to {\rm Alg}_{{\rm Disk}^\sqcup_n}
\]
whose essential image is the full subcategory of locally constant ${\rm Disk}^\sqcup_n$ algebras. 
\end{thm}

@@

Recall the overall strategy.
First, we define a factorization algebra $\clies(\Omega^* \otimes \fg, (\bU_n \fh)_f)$ as a kind of convolution factorization algebra.
Then we get to the heart of the construction:
we show that this convolution algebra naturally sits inside a centralizer diagram.
By the universal property of the centralizer, we then obtain 
a canonical map 
\[
\theta_{{\bf f}}: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  \bZ(\mathbf{f})
\]
where $\bZ_n(\mathbf{f})$ is some locally constant factorization algebra that models the centralizer ${\frak Z}_n(f)$ of the map~$f$.
It is then a direct computation to verify $\theta_f$ is a quasi-isomorphism,
using the Francis-Lurie result mentioned earlier.

@@

\owen{Please read and comment if it is too fast or cryptic (or wrong due, e.g., to sloppy shifts).}

We assume the reader is familiar with Lie algebras and $L_\infty$ algebras and with standard constructions,
such as the Chevalley-Eilenberg chains or cochains, which we may also call the Lie algebra (co)chains.
A nice reference is \owen{Loday-Vallette???}
Nonetheless, we review a few aspects that play a crucial role below.

@@

This coalgebra is canonically coaugmented by the inclusion of the base field $k \xto{\simeq} \Sym^0(\fg[1])$.
There is thus a subcoalgebra $\overline{\cliels(\fg)} \subset \cliels(\fg)$ given by the direct sum over positive symmetric powers of $\fg[1]$,
which can be identified with both the kernel of the counit map as well as cokernel of the coaugmentation map.
In short,
\[
\cliels(\fg) = k \oplus \overline{\cliels(\fg)}
\]
as complexes.

@@

\owen{Probably need to mention somewhere that it's better to work with $\clies(\fg)$ as a completed object.}

@@

Our goal here is to construct the factorization algebra that models the centralizer.
First, we need to show that there is a well-defined functor (in the 1-categorical sense) ${\rm Opens}_{\RR^n} \to \Ch_k$ assigning $\clies(\Omega^*(V) \otimes \fg, \bU_n \fh(V))$ to each open set $V$.
Once that is in place, it is straightforward to describe the structure maps of the prefactorization algebra and to verify it forms a factorization algebra.

@@

Consider now a fixed open set $V \subset \RR^n$.
Then the $L_\infty$ map $f: \fg \rightsquigarrow \fh$ induces canonically an $L_\infty$ map 
\[
\tilde{f}: \Omega^*_c(V) \otimes \fg \rightsquigarrow \Omega^*_c(V) \otimes \fh
\]
by base change along the map $k \to \Omega^*_c(V)$ of dg commutative algebras,
as the compactly supported de Rham forms form a dg commutative algebra under wedge product.
In consequence, we see that $\Omega^*_c(V) \otimes \fg$ acts on $\Omega^*_c(V) \otimes \fh$ and hence equips it with the structure of an $L_\infty$ module over $\Omega^*_c(V) \otimes \fg$.
We denote this module as
\[
(\Omega^*_c(V) \otimes \fh)_f
\]
to emphasize the dependence on the original map~$f$.
In this action, the wedge product of forms intertwines with the $L_\infty$ structure on $\fg$ in a very simple way: 
they simply happen side by side, but do not affect each other.

Observe that $\Omega^*_c(V)$ is a module over the dg commutative algebra $\Omega^*(V)$ of {\em non}\/compactly supported forms.
This action extends immediately to the module $(\Omega^*_c(V) \otimes \fh)_f$, 
so we now view it as an $L_\infty$ module over $\Omega^*(V) \otimes \fg$ as well.
We now need to explain how to make $\cliels(\Omega^*_c(V) \otimes \fh)$ into an $L_\infty$-module over $\Omega^*(V) \otimes \fg$.
Here we rely on the fact that modules over an $L_\infty$ algebra are symmetric monoidal over $\otimes_k$, 
so that we can construct new modules from a given module by taking symmetric powers.
Since
\[
\cliels(\Omega^*_c(V) \otimes \fh) = \bigoplus_{n \geq 0} \Sym^n(\Omega^*_c(V) \otimes \fh[1])
\]
as cochain complexes,
we see that $\cliels(\Omega^*_c(V) \otimes \fh)$ acquires a canonical action of $\Omega^*(V) \otimes \fg$.
In consequence, we have a cochain complex
\[
\clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f)
\]
on each open set~$V$.

The next step is to verify functoriality of this construction over the poset of opens.
This property follows quickly from the fact that wedge product of forms preserves support.
Given an inclusion $i: V' \subset V$ of opens, if we take a form $\alpha \in \Omega^*(V)$ and a compactly supported form $\beta \in \Omega^*_c(V')$, then the wedge product $\alpha \wedge i_* \beta \in \Omega^*_c(V)$ after applying the extension-by-zero map $i_*: \Omega^*_c(V') \to \Omega^*_c(V)$ equals the wedge product $i_*(i^*\alpha \wedge \beta)$ arising from the restriction $i^* \alpha$ of $\alpha$ to~$V'$.
In consequence, the action of $\Omega^*(V) \otimes \fg$ on $\cliels(\Omega^*_c(V') \otimes \fh)_f$ arising from the restriction map $\Omega^*(V) \otimes \fg \to \Omega^*(V') \otimes \fg$ of $L_\infty$ algebras agrees with action induced by the inclusion of $\cliels(\Omega^*_c(V') \otimes \fh)_f$ as a (strict) submodule of~$\cliels(\Omega^*_c(V) \otimes \fh)_f$.
This argument is manifestly associative under composition of inclusions, so we have shown our first claim.

\begin{lmm}
The assignment
\[
V \mapsto \clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f)
\]
determines a functor from ${\rm Opens}_{\RR^n}$ to~$\Ch_k$.
\end{lmm}

@@

The key fact is that the functors $\cliels$ and $\clies$ are suitably symmetric monoidal:
they send a product of $L_\infty$ algebras to a tensor product of cochain complexes.
Hence it suffices to examine the underlying functors to $L_\infty$ algebras.
As the functors $\Omega^*$ and $\Omega^*_c$ send finite disjoint unions of opens to the direct product of cochain complexes, 
the functors like $\Omega^* \otimes \fg$ and $\Omega^*_c \otimes \fh$ send finite disjoint unions of opens to products of $L_\infty$ algebras.
In consequence, we obtain the desired second claim.

\begin{lmm}
The assignment
\[
V \mapsto \clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f)
\]
determines a prefactorization algebra, i.e., a strict algebra over ${\rm Opens}_{\RR^n}^\sqcup$ with values in~$\Ch_k^\otimes$.
\end{lmm}

Due to the Poincar\'e lemma, the inclusion of a disk into a bigger disk $D \hookrightarrow D'$ makes the structure map 
\[
\clies(\Omega^*(D) \otimes \fg, \cliels(\Omega^*_c(D) \otimes \fh)_f) \xto{\simeq} \clies(\Omega^*(D) \otimes \fg, \cliels(\Omega^*_c(D) \otimes \fh)_f)
\]
a quasi-isomorphism.
Hence this prefactorization algebra is locally constant in a homotopical sense.

@@

\begin{dfn}
\label{dfn: centralizer for f}
Let $\clies(\Omega^* \otimes \fg, (\bU_n \fh)_f)$ denote this factorization algebra on $\RR^n$ arising from the map $f: \fg \rightsquigarrow \fh$.
\end{dfn}

\begin{rmk}
For those coming from an operadic background, it may be helpful to recognize that our approach is a variant of a familiar convolution construction.
The functor $\bU_n \fh = \cliels(\Omega^*_c \otimes \fh)$ determines an algebra over the colored operad ${\rm Opens}_{\RR^n}^\sqcup$,
while the functor $\cliels(\Omega^* \otimes \fg)$ determines a {\em co}\/algebra over the colored operad ${\rm Opens}_{\RR^n}^\sqcup$.
The algebra $\clies(\Omega^* \otimes \fg, (\bU_n \fh)_f)$ assigns the graded vector space
\[
\Hom^\bullet(\cliels(\Omega^*(V) \otimes \fg), \cliels(\Omega^*_c(V) \otimes \fh))
\] 
to each open set $V$,
twining together this coalgebra and algebra.
\owen{This has a name, but I'm blanking at the moment.}
The differential can be seen as a twisting cocycle arising from a choice of map $f$;
there is a natural basepoint to the space of differentials on this graded vector space by taking the usual differential of a hom-complex.
\end{rmk}

@@

Our goal in this subsection is to construct a map of factorization algebras
\[
\ev_{{\bf f}}: \clies(\Omega^* \otimes \fg, (\Omega^*_c \otimes \fh)_f) \otimes \bU_n \fg \to \bU_n \fh,
\]
while in the next subsection we will show it fits into a centralizer diagram.
To produce our map, we first construct it separately on each open subset and then explain why the construction is functorial.

Let $V \subset \RR^n$ be open.
The canonical pairing between Lie algebra chains and cochains provides a canonical cochain map
\[
\clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f) \otimes \cliels(\Omega^*(V) \otimes \fg) \to \cliels(\Omega^*_c(V) \otimes \fh)_f.
\]
The canonical inclusion $\Omega^*_c(V) \otimes \fg \hookrightarrow \Omega^*(V) \otimes \fg$ induces a canonical inclusion 
\[
\cliels(\Omega^*_c(V) \otimes \fg) \hookrightarrow \cliels(\Omega^*(V) \otimes \fg)
\]
and hence, precomposing this inclusion with the pairing, we obtain our desired map
\[
\ev_{{\bf f}}(V): \clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f) \otimes \bU_n \fg(V) \to \bU_n \fh(V)
\]
for each open~$V$.

@@

%any element of $\cliels\big(\fg \otimes \Omega^* , B\big)$ 

@@

%\begin{equation} \label{eqdef:ev} \begin{array}{c}\ev: Sym^p \big( \fg \otimes \Omega^* (U)[-1] ,B(U)\big)
%\otimes  Sym^p( \fg\otimes \Omega^*_c(U) [1]) \stackrel{ev}\longrightarrow B(U)  

@@

% $\mathbf{1}\in \clies(\fg\otimes \Omega^*, B) )$ which is the unit $k\to \clies(\fg\otimes \Omega^*, B) )$

@@

%   \clies\big(\fg\otimes \Omega^*, B\big)  \, \cong \, k \oplus \overline{ \clies(\fg\otimes \Omega^*, B) )}

@@

% \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, 

@@

% \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, \bigoplus\limits_{J\subset I} {\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big) 

@@

%{\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big) = 

@@

%We think of an element of ${\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ has an element of ${\clies}\big(\fg\otimes \Omega^*(U), B(U)\big)$

@@

%${\clies}^{(\emptyset)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ corresponding to the empty family.

@@

%$X= \bigotimes\limits_{i\in I} X_i \in \bigotimes\limits_{I}\cliels(\fg\otimes \Omega_c^*(U_i)) \cong \cliels(\fg\otimes \Omega^*_c(U))$, we 

@@

We need to show that this natural transformation extends to a morphism of prefactorization algebras,
i.e., that it intertwines with the operations over the colored operad ${\rm Opens}_{\RR^n}^\sqcup$.
Here we use the fact that the evaluation pairing between Lie algebra chains and cochains plays nicely with products of $L_\infty$ algebras, in the following sense.
Let $\fX, \fY$ be $L_\infty$ algebras and let $M, N$ be modules for those respective $L_\infty$ algebras.
The direct sum $M \oplus N$ admits a natural action of the product $L_\infty$ algebra $\fX \times \fY$.
Then the isomorphisms
\begin{align*}
\clies(\fX \times \fY, M \oplus N) \otimes \cliels(\fX \times \fY) 
&\cong (\clies(\fX, M) \otimes \clies(\fY,N) ) \otimes (\cliels(\fX) \otimes \cliels(\fY) ) \\
&\cong (\clies(\fX,M) \otimes \cliels(\fX) ) \otimes (\cliels(\fY,N) \otimes \cliels(\fY) )
\end{align*}
precompose with the tensored evaluation pairings
\[
\cong (\clies(\fX,M) \otimes \cliels(\fX) ) \otimes (\cliels(\fY,N) \otimes \cliels(\fY) ) \xto{\ev_\fX \otimes \ev_\fY} M \otimes N
\]
to provide a canonical map
\[
\clies(\fX \times \fY, M \oplus N) \otimes \cliels(\fX \times \fY) \to M \otimes N.
\]
In light of this observation and the fact that functors such as $\Omega^* \otimes \fg$ and $\Omega^*_c \otimes \fh$ send disjoint unions to products of $L_\infty$ algebras,
we deduce the desired result.

@@

\subsection{Abelian Lie algebras and an $\EE_n$ HKR theorem}

>>>>

Our work here relies on a concrete and convenient model for these enveloping $\EE_n$ algebras by factorization algebras.
In particular, thanks again to \cite{Knudsen}, 
we know that the $\EE_n$ enveloping algebra $\UU_n \fg$ admits a model $\bU_n \fg$ whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^*(V) \otimes \fg)$ to each open set~$V$.
There is another factorization algebra whose underlying assigns $\clies(\Omega^\bu(V) \otimes \fg)$ to each open~$V$.
Our paper shows that such factorization algebras model other important $\EE_n$ algebras, notably centralizers.

\begin{thm}
\label{thm: centralizer}
Let $\fg$ and $\fh$ be $L_\infty$ algebras over the real or complex numbers, 
and let $f: \fg \rightsquigarrow \fh$ be a homotopy-coherent morphism of $L_\infty$ algebras
(i.e., a map of conilpotent cocommutative coalgebras $f: \cliels(\fg) \to \cliels(\fh)$).
This map determines functorially a map of $\EE_n$ algebras
\[
\UU_n f: \UU_n \fg \to \UU_n \fh
\]
between their enveloping $\EE_n$ algebras.
The centralizer of this map ${\frak Z}_n(\UU_n f)$ is an $\EE_n$ algebra modeled by the factorization algebra 
\[
\clies(\Omega^\bu \otimes \fg, \cliels(\Omega^\bu_c \otimes \fh)_f)
\]
equipped with a convolution-type product,
where the subscript $f$ indicates how $\cliels(\Omega^\bu_c \otimes \fh)$ is a module over $\Omega^\bu \otimes \fg$.
\end{thm}

@@

\begin{cor}
\label{thm: center}
The center ${\frak Z}_n(\fg)$ of the enveloping $\EE_n$ algebra $\UU_n\fg$ is the $\EE_n$ algebra $\clies(\fg, \UU_n\fg)$. 
When $k$ is $\RR$ or $\CC$, the 
center is modeled by the locally constant factorization algebra that assigns
\[
\clies(\fg \otimes \Omega^\bu(U), \cliels( \fg \otimes \Omega^\bu_c(U)))
\]
to each open set $U \subset \RR^n$.
\end{cor}

This result generalizes the fact that $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$, 
since the associative algebra $U\fg$ is modeled by the locally constant one-dimensional factorization algebra that assigns
$\cliels (\fg \otimes \Omega^\bu_c(U))$ to each open $U \subset \RR$.

@@

\begin{cor}
\label{thm: koszul duality}
The centralizer of the augmentation $\epsilon: \UU_n \fg \to k$ is equivalent to $\clies(\fg)$ viewed as an $\EE_n$ algebra. It is modeled by the locally constant factorization algebra that assigns
\[
\clies(\fg \otimes \Omega^\bu(V))
\]
to each open set $V \subset \RR^n$.
\end{cor}

@@

Having an explicit presentation for the centralizer of a map of $\EE_n$ algebras leads to a calculation of factorization homology.
The enveloping $\EE_n$ algebra is the homotopy $O(n)$-fixed points, or a $\mathrm{Disk}_n$ algebra in the sense of~\cite{AF},
and hence determines a factorization algebra on any un-oriented $n$-dimensional manifold \cite{Knudsen}.
Therefore, for a closed $n$-dimensional manifold $M$, one has
\[
\int_M {\frak Z}_n(\UU_n \rho) \simeq \clies(\fg \otimes \Omega^\bu(M), \cliels( \fh \otimes \Omega^\bu(M))).
\]
Since $\Omega^\bu(S^n) \simeq \CC[\epsilon_n]$, where $\epsilon_n$ is a formal variable with $|\epsilon_n| = n$ and $\epsilon_n^2 = 0$, we have
\[
\int_{S^n} {\frak Z}_n(\UU_n \rho) \simeq \clies(\fg[\epsilon_n], \cliels( \fh[\epsilon_n]))
\]
For $n=1$, this recovers a theorem of Tamarkin and Tsygan \cite{TT} on the Hochschild cohomology of differential operators on a Lie group $G$;
see Example~\ref{eg: TT}.

@@

\begin{thm}[\cite{LurieHA} Proposition 5.4.5.15]
\label{thm:lurie1} 
There is a fully faithful embedding of $\infty$-categories
\[
{\rm Alg}_{\EE_n} \to {\rm Alg}_{{\rm Disk}^\sqcup_n}
\]
whose essential image is the full subcategory of locally constant ${\rm Disk}^\sqcup_n$ algebras. 
\end{thm}

@@

Recall the overall strategy.
First, we define a factorization algebra $\clies(\Omega^\bu \otimes \fg, (\bU_n \fh)_f)$ as a kind of convolution factorization algebra.
Then we get to the heart of the construction:
we show that this convolution algebra naturally sits inside a centralizer diagram.
By the universal property of the centralizer, we then obtain 
a canonical map 
\[
\theta_{{\bf f}}: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  \bZ(\mathbf{f})
\]
where $\bZ_n(\mathbf{f})$ is some locally constant factorization algebra that models the centralizer ${\frak Z}_n(f)$ of the map~$f$.
It is then a direct computation to verify $\theta_f$ is a quasi-isomorphism,
using the Francis-Lurie result mentioned earlier.

@@

We assume the reader is familiar with Lie algebras and $L_\infty$ algebras and with standard constructions,
such as the Chevalley-Eilenberg chains or cochains, which we may also call the Lie algebra (co)chains.
A nice reference is \cite{LodayVallette}.
Nonetheless, we review a few aspects that play a crucial role below.

@@

This coalgebra is canonically coaugmented by the inclusion of the base field $k \xto{\simeq} \Sym^0(\fg[1])$.
There is thus a subcoalgebra $\overline{\cliels(\fg)} \subset \cliels(\fg)$ given by the direct sum over positive symmetric powers of $\fg[1]$,
which can be identified with both the kernel of the counit map as well as cokernel of the coaugmentation map.
In short,
\[
\cliels(\fg) = k \oplus \overline{\cliels(\fg)}
\]
as cochain complexes.

@@

\owen{Probably need to mention somewhere that it's better to work with $\clies(\fg)$ as a completed object.}
\brian{I think you've got around this issue by talking about Homs}

@@

Our goal here is to construct the factorization algebra that models the centralizer.
First, we need to show that there is a well-defined functor (in the 1-categorical sense) ${\rm Opens}_{\RR^n} \to \Ch_k$ assigning $\clies(\Omega^\bu(V) \otimes \fg, \bU_n \fh(V))$ to each open set $V$.
Once that is in place, it is straightforward to describe the structure maps of the prefactorization algebra and to verify it forms a factorization algebra.

@@

Consider now a fixed open set $V \subset \RR^n$.
Then the $L_\infty$ map $f: \fg \rightsquigarrow \fh$ induces canonically an $L_\infty$ map 
\[
\tilde{f}: \Omega^\bu_c(V) \otimes \fg \rightsquigarrow \Omega^\bu_c(V) \otimes \fh
\]
by base change along the map $k \to \Omega^\bu_c(V)$ of dg commutative algebras,
as the compactly supported de Rham forms form a dg commutative algebra under wedge product.
In consequence, we see that $\Omega^\bu_c(V) \otimes \fg$ acts on $\Omega^\bu_c(V) \otimes \fh$ and hence equips it with the structure of an $L_\infty$ module over $\Omega^\bu_c(V) \otimes \fg$.
We denote this module as
\[
(\Omega^\bu_c(V) \otimes \fh)_f
\]
to emphasize the dependence on the original map~$f$.
In this action, the wedge product of forms intertwines with the $L_\infty$ structure on $\fg$ in a very simple way: 
they simply happen side by side, but do not affect each other.

Observe that $\Omega^\bu_c(V)$ is a module over the dg commutative algebra $\Omega^\bu(V)$ of {\em non}\/compactly supported forms.
This action extends immediately to the module $(\Omega^\bu_c(V) \otimes \fh)_f$, 
so we now view it as an $L_\infty$ module over $\Omega^\bu(V) \otimes \fg$ as well.
We now need to explain how to make $\cliels(\Omega^\bu_c(V) \otimes \fh)$ into an $L_\infty$-module over $\Omega^\bu(V) \otimes \fg$.
Here we rely on the fact that modules over an $L_\infty$ algebra are symmetric monoidal over $\otimes_k$, 
so that we can construct new modules from a given module by taking symmetric powers.
Since
\[
\cliels(\Omega^\bu_c(V) \otimes \fh) = \bigoplus_{n \geq 0} \Sym^n(\Omega^\bu_c(V) \otimes \fh[1])
\]
as cochain complexes,
we see that $\cliels(\Omega^\bu_c(V) \otimes \fh)$ acquires a canonical action of $\Omega^\bu(V) \otimes \fg$.
In consequence, we have a cochain complex
\[
\clies(\Omega^\bu(V) \otimes \fg, \cliels(\Omega^\bu_c(V) \otimes \fh)_f)
\]
on each open set~$V$.

The next step is to verify functoriality of this construction over the poset of opens.
This property follows quickly from the fact that wedge product of forms preserves support.
Given an inclusion $i: V' \subset V$ of opens, if we take a form $\alpha \in \Omega^\bu(V)$ and a compactly supported form $\beta \in \Omega^\bu_c(V')$, then the wedge product $\alpha \wedge i_* \beta \in \Omega^\bu_c(V)$ after applying the extension-by-zero map $i_*: \Omega^\bu_c(V') \to \Omega^\bu_c(V)$ equals the wedge product $i_*(i^*\alpha \wedge \beta)$ arising from the restriction $i^* \alpha$ of $\alpha$ to~$V'$.
In consequence, the action of $\Omega^\bu(V) \otimes \fg$ on $\cliels(\Omega^\bu_c(V') \otimes \fh)_f$ arising from the restriction map $\Omega^\bu(V) \otimes \fg \to \Omega^\bu(V') \otimes \fg$ of $L_\infty$ algebras agrees with action induced by the inclusion of $\cliels(\Omega^\bu_c(V') \otimes \fh)_f$ as a (strict) submodule of~$\cliels(\Omega^\bu_c(V) \otimes \fh)_f$.
This argument is manifestly associative under composition of inclusions, so we have shown our first claim.

\begin{lmm}
The assignment
\[
V \mapsto \clies(\Omega^\bu(V) \otimes \fg, \cliels(\Omega^\bu_c(V) \otimes \fh)_f)
\]
determines a functor from ${\rm Opens}_{\RR^n}$ to~$\Ch_k$.
\end{lmm}

@@

The key fact is that the functors $\cliels$ and $\clies$ are suitably symmetric monoidal:
they send a product of $L_\infty$ algebras to a tensor product of cochain complexes.
Hence it suffices to examine the underlying functors to $L_\infty$ algebras.
As the functors $\Omega^\bu$ and $\Omega^\bu_c$ send finite disjoint unions of opens to the direct product of cochain complexes, 
the functors like $\Omega^\bu \otimes \fg$ and $\Omega^\bu_c \otimes \fh$ send finite disjoint unions of opens to products of $L_\infty$ algebras.
In consequence, we obtain the desired second claim.

\begin{lmm}
The assignment
\[
V \mapsto \clies(\Omega^\bu(V) \otimes \fg, \cliels(\Omega^\bu_c(V) \otimes \fh)_f)
\]
determines a prefactorization algebra, i.e., a strict algebra over ${\rm Opens}_{\RR^n}^\sqcup$ with values in~$\Ch_k^\otimes$.
\end{lmm}

Due to the Poincar\'e lemma, the inclusion of a disk into a bigger disk $D \hookrightarrow D'$ makes the structure map 
\[
\clies(\Omega^\bu(D) \otimes \fg, \cliels(\Omega^\bu_c(D) \otimes \fh)_f) \xto{\simeq} \clies(\Omega^\bu(D) \otimes \fg, \cliels(\Omega^\bu_c(D) \otimes \fh)_f)
\]
a quasi-isomorphism.
Hence this prefactorization algebra is locally constant in a homotopical sense.

@@

\begin{dfn}
\label{dfn: centralizer for f}
Let $\clies(\Omega^\bu \otimes \fg, (\bU_n \fh)_f)$ denote this factorization algebra on $\RR^n$ arising from the map $f: \fg \rightsquigarrow \fh$.
\end{dfn}

\begin{rmk}
For those coming from an operadic background, it may be helpful to recognize that our approach is a variant of a familiar convolution construction.
The functor $\bU_n \fh = \cliels(\Omega^\bu_c \otimes \fh)$ determines an algebra over the colored operad ${\rm Opens}_{\RR^n}^\sqcup$,
while the functor $\cliels(\Omega^\bu \otimes \fg)$ determines a {\em co}\/algebra over the colored operad ${\rm Opens}_{\RR^n}^\sqcup$.
The algebra $\clies(\Omega^\bu \otimes \fg, (\bU_n \fh)_f)$ assigns the graded vector space
\[
\Hom^\bullet(\cliels(\Omega^\bu(V) \otimes \fg), \cliels(\Omega^\bu_c(V) \otimes \fh))
\] 
to each open set $V$,
twining together this coalgebra and algebra.
\owen{This has a name, but I'm blanking at the moment.}
\brian{convolution?}
The differential can be seen as a twisting cocycle arising from a choice of map $f$;
there is a natural basepoint to the space of differentials on this graded vector space by taking the usual differential of a hom-complex.
\end{rmk}

@@

Our goal in this subsection is to construct a map of factorization algebras
\[
\ev_{{\bf f}}: \clies(\Omega^\bu \otimes \fg, (\Omega^\bu_c \otimes \fh)_f) \otimes \bU_n \fg \to \bU_n \fh,
\]
while in the next subsection we will show it fits into a centralizer diagram.
To produce our map, we first construct it separately on each open subset and then explain why the construction is functorial.

Let $V \subset \RR^n$ be open.
The canonical pairing between Lie algebra chains and cochains provides a canonical cochain map
\[
\clies(\Omega^\bu(V) \otimes \fg, \cliels(\Omega^\bu_c(V) \otimes \fh)_f) \otimes \cliels(\Omega^\bu(V) \otimes \fg) \to \cliels(\Omega^\bu_c(V) \otimes \fh)_f.
\]
The canonical inclusion $\Omega^\bu_c(V) \otimes \fg \hookrightarrow \Omega^\bu(V) \otimes \fg$ induces a canonical inclusion 
\[
\cliels(\Omega^\bu_c(V) \otimes \fg) \hookrightarrow \cliels(\Omega^\bu(V) \otimes \fg)
\]
and hence, precomposing this inclusion with the pairing, we obtain our desired map
\[
\ev_{{\bf f}}(V): \clies(\Omega^\bu(V) \otimes \fg, \cliels(\Omega^\bu_c(V) \otimes \fh)_f) \otimes \bU_n \fg(V) \to \bU_n \fh(V)
\]
for each open~$V$.

@@

%any element of $\cliels\big(\fg \otimes \Omega^\bu , B\big)$ 

@@

%\begin{equation} \label{eqdef:ev} \begin{array}{c}\ev: Sym^p \big( \fg \otimes \Omega^\bu (U)[-1] ,B(U)\big)
%\otimes  Sym^p( \fg\otimes \Omega^\bu_c(U) [1]) \stackrel{ev}\longrightarrow B(U)  

@@

% $\mathbf{1}\in \clies(\fg\otimes \Omega^\bu, B) )$ which is the unit $k\to \clies(\fg\otimes \Omega^\bu, B) )$

@@

%   \clies\big(\fg\otimes \Omega^\bu, B\big)  \, \cong \, k \oplus \overline{ \clies(\fg\otimes \Omega^\bu, B) )}

@@

% \clies\big(\fg\otimes \Omega^\bu(U), B(U)\big)  \, \cong \, 

@@

% \clies\big(\fg\otimes \Omega^\bu(U), B(U)\big)  \, \cong \, \bigoplus\limits_{J\subset I} {\clies}^{(J)}\big(\fg\otimes \Omega^\bu(U), B(U)\big) 

@@

%{\clies}^{(J)}\big(\fg\otimes \Omega^\bu(U), B(U)\big) = 

@@

%We think of an element of ${\clies}^{(J)}\big(\fg\otimes \Omega^\bu(U), B(U)\big)$ has an element of ${\clies}\big(\fg\otimes \Omega^\bu(U), B(U)\big)$

@@

%${\clies}^{(\emptyset)}\big(\fg\otimes \Omega^\bu(U), B(U)\big)$ corresponding to the empty family.

@@

%$X= \bigotimes\limits_{i\in I} X_i \in \bigotimes\limits_{I}\cliels(\fg\otimes \Omega_c^*(U_i)) \cong \cliels(\fg\otimes \Omega^\bu_c(U))$, we 

@@

We need to show that this natural transformation extends to a morphism of prefactorization algebras,
i.e., that it intertwines with the operations over the colored operad ${\rm Opens}_{\RR^n}^\sqcup$.
Here we use the fact that the evaluation pairing between Lie algebra chains and cochains plays nicely with products of $L_\infty$ algebras, in the following sense.
Let $\fX, \fY$ be $L_\infty$ algebras and let $M, N$ be modules for those respective $L_\infty$ algebras.
The direct sum $M \oplus N$ admits a natural action of the product $L_\infty$ algebra $\fX \times \fY$.
Then the isomorphisms
\begin{align*}
\clies(\fX \times \fY, M \oplus N) \otimes \cliels(\fX \times \fY) 
&\cong (\clies(\fX, M) \otimes \clies(\fY,N) ) \otimes (\cliels(\fX) \otimes \cliels(\fY) ) \\
&\cong (\clies(\fX,M) \otimes \cliels(\fX) ) \otimes (\cliels(\fY,N) \otimes \cliels(\fY) )
\end{align*}
precompose with the tensored evaluation pairings
\[
\cong (\clies(\fX,M) \otimes \cliels(\fX) ) \otimes (\cliels(\fY,N) \otimes \cliels(\fY) ) \xto{\ev_\fX \otimes \ev_\fY} M \otimes N
\]
to provide a canonical map
\[
\clies(\fX \times \fY, M \oplus N) \otimes \cliels(\fX \times \fY) \to M \otimes N.
\]
In light of this observation and the fact that functors such as $\Omega^\bu \otimes \fg$ and $\Omega^\bu_c \otimes \fh$ send disjoint unions to products of $L_\infty$ algebras,
we deduce the desired result.

@@

\subsection{Abelian Lie algebras and an $\EE_n$ Hochschild-Kostant-Rosenberg theorem}
